Reducing iptables configuration complexity using chains

### 2014-05-03 iptables/paper.tex
add example definition

\section{Optimizing configuration with an example setup}
\subsection{Actual configuration}

>>>>

\section{Optimizing configuration with an example setup}
\subsection{Example definition}
\begin{itemize}
  \item A web service should be available from all networks (i.e. internet) on port 80 (http) and 443 (https)
  \item The server can be managed remotely using ssh (port 20) and webmin (port 10000), but only from a limited set of IP addresses (admin PC's).
  \item The server hosts a samba service (several TCP ports), that should only be available from a limited set of IP addresses (admin + webmaster PC's).
  \item Outgoing connections will be filtered, but some services should be allowed (dns, dhcp, smtp, ntp) and some external websites should be available to get updates.
\end{itemize}

\subsection{Actual configuration}
